Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-14 output/paper/_figures.qmd
Moved some tables to SI. Added better captions for tables and figures.

# Main results

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Average comparisons
#| fig-width: 6
#| fig-height: 7

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 9
#| fig-height: 10

@@

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Average comparisons
#| fig-width: 5
#| fig-height: 5

>>>>

# Figures for main results

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal comparison results for $hitrtse \sim edc$
#| fig-width: 6
#| fig-height: 7

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Marginal comparison results for $metabolite \sim edc$
#| fig-width: 9
#| fig-height: 10

@@

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal comparison results for $hitrtse \sim metabolite$
#| fig-width: 5
#| fig-height: 5

### 2023-12-14 output/paper/_si.qmd
Moved some tables to SI. Added better captions for tables and figures.

## Descriptive data

@@

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
Codebook for covariates used in RQ1
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
Codebook for covariates used in RQ2
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
Codebook for covariates used in RQ3
:::

@@

## Other results

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Weights
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Weights
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Weights
:::

@@

## Descriptive data

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
Description of chemicals
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest()$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
Description of metabolites
:::

## Main results

@@

exposures_of_interest <- c(
  "cortisol production",
  "X11bHSD"
)
ret_adrfs <- lapply(
  exposures_of_interest, function(x) {
    plot_adrf(
      df_preds = marginal_gcomp_3 |>
        tidylog::filter(
          variable == x
        )
    )
  }
)
ret_adrfs[[1]]
#ret_adrfs[[2]]
```
Average dose-response functions for RQ3
:::

## Other results

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Average comparisons for effect modification
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Average comparisons for effect modification
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Average comparisons for effect modification
:::

>>>>

## Tables for descriptive data

@@

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
Codebook for covariates used in $hitrtse \sim edc$
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
Codebook for covariates used in $metabolite \sim edc$
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
Codebook for covariates used in $hitrtse \sim metabolite$
:::

@@

## Tables for main results

### Balancing weights

```{r}
targets::tar_load(
  dplyr::matches("balance_(\\d)$"),
  store = store
)
```

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $hitrtse \sim edc$
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $metabolite \sim edc$
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $hitrtse \sim metabolite$
:::

```{r}
targets::tar_load(
  dplyr::matches("weights_(\\d)$"),
  store = store
)
```

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim edc$
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $metabolite \sim edc$
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim metabolite$
:::

## Tables for other results

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim edc \times sex$
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $metabolite \sim edc \times sex$
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim metabolite \times sex$
:::

@@

## Figures for descriptive data

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
Classification of the measured non-persistent EDCs, by cohort.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
Classification of the measured corticosteroids, by cohort.
:::

## Figures for main results

@@

exposures_of_interest <- c(
  "cortisol production",
  "X11bHSD"
)
ret_adrfs <- lapply(
  exposures_of_interest, function(x) {
    plot_adrf(
      df_preds = marginal_gcomp_3 |>
        tidylog::filter(
          variable == x
        )
    )
  }
)
ret_adrfs[[1]]
#ret_adrfs[[2]]
```
Average dose-response functions for...
:::

## Figures for other results

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $metabolite \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim metabolite \times sex$
:::

### 2023-12-14 output/paper/_tables.qmd
Nothing.
Moved some tables to SI. Added better captions for tables and figures.

# Descriptive data

@@

# Main results

## Balancing weights

```{r}
targets::tar_load(
  dplyr::matches("balance_(\\d)$"),
  store = store
)
```

```{r balance-1}
#| label: tbl-balance-1
#| tbl-cap: Effective number of observations

balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```

```{r balance-2}
#| label: tbl-balance-2
#| tbl-cap: Effective number of observations

balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```

```{r balance-3}
#| label: tbl-balance-3
#| tbl-cap: Effective number of observations

balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```

```{r}
targets::tar_load(
  dplyr::matches("weights_(\\d)$"),
  store = store
)
```

```{r weights-1}
#| label: tbl-weights-1
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```

```{r weights-2}
#| label: tbl-weights-2
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```

```{r weights-3}
#| label: tbl-weights-3
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```

@@

```{r marginal-1}
#| label: tbl-marginal-1
#| tbl-cap: Average comparisons

@@

```{r marginal-2}
#| label: tbl-marginal-2
#| tbl-cap: Average comparisons

@@

```{r marginal-3}
#| label: tbl-marginal-3
#| tbl-cap: Average comparisons

@@

# Other analyses

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing for effect modification

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing for effect modification

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing for effect modification

>>>>

# Tables for descriptive data

@@

# Tables for main results

@@

```{r marginal-1}
#| label: tbl-marginal-1
#| tbl-cap: Marginal comparison results for $hitrtse \sim edc$

@@

```{r marginal-2}
#| label: tbl-marginal-2
#| tbl-cap: Marginal comparison results for $metabolite \sim edc$

@@

```{r marginal-3}
#| label: tbl-marginal-3
#| tbl-cap: Marginal comparison results for $hitrtse \sim metabolite$

@@

# Tables for other analyses

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim edc$

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing results of effect modification by sex for $metabolite \sim edc$

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim metabolite$

### 2023-12-14 output/paper/manuscript.qmd
Transformed into R package cause I wanted to use roxygen2 to document functions but it does not seem to be working. Renamed directory code to R for same reason. Removed virtually all default arguments functions. Testing pipelines.
Moved some tables to SI. Added better captions for tables and figures.

```{r vars-methods}
source(here::here("code/dictionaries.R"))
source(here::here("code/data.R"))
source(here::here("code/proc_res.R"))

@@

- Discuss limitations of the study, taking into account sources of potential bias or imprecision.
- Discuss both direction and magnitude of any potential bias.

@@

>>>>

```{r vars-methods}
source(here::here("R/dictionaries.R"))
source(here::here("R/data.R"))
source(here::here("R/proc_res.R"))

@@

@@

These findings should be interpreted in light of the following limitations and strengths.

Strengths of the present study include...
